Contracts for Contracts

### 2023-06-26 paper/formal_model.tex
still need conditional

The body of functions is simply a statement.
Statements can be a type-and-identifier declaration (without providing an initial
value), an expression (e.g. calling a function for its side effects), a
composition of two statements, an assignment, a \Keywd{return} statement, or a \Keywd{revert} statement.
The left-hand side part of assignments (i.e. assignable) can be either
a type-and-type declaration, an identifier, or a projection of mappings or structs.
Since \corelang permits both mappings and structs, which can recursively referring
other types, projection allows use to directly access nested data structures,
e.g. \code{v.field1[0].field2}.
A \Keywd{revert} statement aborts the execution, reverting any changes made to
the blockchain state.

>>>>

The body of functions is simply a statement.
Statements can be a type-and-identifier declaration (without providing an initial
value), an expression (e.g. calling a function for its side effects), a
composition of two statements, an assignment, a \Keywd{return} statement, a \Keywd{revert} statement,
or a conditional statement.
The left-hand side part of assignments (i.e. assignable) can be either
a type-and-type declaration, an identifier, or a projection of mappings or structs.
Since \corelang permits both mappings and structs, which can recursively referring
other types, projection allows use to directly access nested data structures,
e.g. \code{v.field1[0].field2}.
A \Keywd{revert} statement aborts the execution, reverting any changes made to
the blockchain state.
